Relative Stable Maps in Genus One via Central Alignments

### 2019-01-01 GenusOneRelativeMaps.tex
Started description of Type A locus. Need to fix notation

\begin{figure}[h]
    \centering
    \begin{minipage}{0.3\textwidth}
        \centering
        \Yagraph
        \caption{$\mathcal Y_A$}
    \end{minipage}\hfill
    \begin{minipage}{0.3\textwidth}
        \centering
        \Ybgraph
        \caption{$\mathcal Y_B$}
    \end{minipage}\hfill
    \begin{minipage}{0.3\textwidth}
        \centering
        \Ycgraph
        \caption{$\Ycal_C^+$}
    \end{minipage}
\end{figure}
\noindent Notice that the continuity of the tropical map identifies all of the edge lengths up to scalars given by the expansion factors (i.e. tangency orders) at the edges; thus the tropical moduli space is isomorphic to $\RR_{\geq 0}$ and so we have a divisor (with no subdivision required).

These divisors live inside an open neighbourhood of the preimage in $\VZ$ of our chosen locus in $\Mcal$, and are thus locally closed substacks of $\VZ$. To obtain the desired components of $\Dcal^k$, we must take the closure of these locally closed substacks. We will analyse this procedure on a case-by-case basis, and see once again that the tropical picture gives a complete and recursive description of the closure.

\subsubsection{Type A} By definition the locus $\Ycal_A$ contains those aligned maps which are in the closure of the locus of maps whose associated tropical curve has the same combinatorial type as Figure 1\footnote{(Navid) Bad LaTeX reference}. We will now argue that such an aligned map is always obtained by giving an alignment on the piece of the curve corresponding to the genus one vertex.

We start by considering possible limiting points of our original locus in $\Mcal$. These correspond to further degenerations of the (combinatorial type of the) tropical map.

>>>>

\begin{figure}[h]
    \centering
    \begin{minipage}{0.3\textwidth}
        \centering
        \Yagraph
        \caption{$\mathcal Y_A$}
    \end{minipage}\hfill
    \begin{minipage}{0.3\textwidth}
        \centering
        \Ybgraph
        \caption{$\mathcal Y_B$}
    \end{minipage}\hfill
    \begin{minipage}{0.3\textwidth}
        \centering
        \Ycgraph
        \caption{$\Ycal_C^+$}
    \end{minipage}
\end{figure}
\noindent Notice that the continuity of the tropical map identifies all of the edge lengths, up to weights given by the expansion factors (i.e. tangency orders) at the edges; thus the tropical moduli space is isomorphic to $\RR_{\geq 0}$ and so we have a divisor (with no subdivision required).

These divisors live inside an open neighbourhood of the preimage in $\VZ$ of our chosen locus in $\Mcal$, and are thus locally closed substacks of $\VZ$. To obtain the desired components of $\Dcal^k$, we must take the closure of these locally closed substacks. We will analyse this procedure on a case-by-case basis, and see once again that the tropical picture gives a complete and recursive description of the combinatorics. As usual, this will be done by comparing loci in$\VZ$ with loci in $\Mcal$. To be more precise: we will take the closure of our locally closed substack in $\Mcal$ and relate it to the closure of our locally closed substack in $\VZ$. We will see that the induced map on closures is another blow-up. The closed locus in $\Mcal$ is understood by \cite{PuncturedMaps} as a fibre product of moduli spaces of punctured maps. \footnote{(Navid) Introduce notation for these locally closed substacks, because this shit is getting out of hand.}

\subsubsection{Type A} By definition the locus $\Ycal_A$ contains those elements of $\VZ$ which appear in the closure of the locus of aligned maps whose associated tropical curve has the same combinatorial type as Figure 1\footnote{(Navid) Bad LaTeX reference}. We will now argue that such an element restricts to give an aligned map on the piece of the curve corresponding to $\mathsq{C}_1$, and that conversely given an aligned map corresponding to $\mathsq{C}_1$ and ordinary punctured maps corresponding to $\mathsq{C}_0,\mathsq{C}_2,\ldots,\mathsq{C}_r$, the glued map is aligned. This shows that $\Ycal_A$ is equal, up to an \'etale quotient, to the fibre product:
\begin{equation*}\M{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right). \end{equation*}
Put differently, the map from the closed locus in $\VZ$ to the closed locus in $\Mcal$ is given by blowing up one of the factors of the fibre product
\begin{equation*}\M{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}. \end{equation*}
and leaving the rest alone.

Let us start by considering possible limiting points of our original locus in $\Mcal$. These correspond to further degenerations of the (combinatorial type of the) tropical map.
